A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-07 paper/ms.tex
update ms
* debugged RotGPtransit
* clarified discussion points

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile appears to be
  asymmetric, and the individual transit times are correlated with the
  local light curve slope.
  We discuss possible explanations for each anomaly.
  More widely applicable though is the fact that the $\delta$~Lyr
  cluster is one of $\sim$10$^3$ clusters whose properties have been
  clarified by Gaia.  Many other exoplanet hosts are candidate
  members of these clusters based on kinematics; their ages can
  be confirmed by using the TESS full frame images to
  measure stellar rotation periods.
\end{abstract}

@@

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{KounkelCovey2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Galactic positions and tangential velocities of stars in the
			$\delta$\,Lyr cluster.} Points are reported cluster members from
		\citet{KounkelCovey2019}.  
		The tangential velocities relative to
		\sn\ (lower-right) are computed assuming that every star has the same
		three-dimensional spatial velocity as \sn.
		Our analysis uses stars (black points)
		in the spatial and kinematic vicinity of Kepler\,1627 (yellow
		star).  The question of whether the other candidate cluster members
		(gray points) are part of the cluster is outside our scope.  The
		location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
		candidate cluster member, selected from the catalog of \citet{KounkelCovey2019} based on its
		position and kinematics.
		Of the \nkinematic\ candidate cluster members, 58 have at least one
		quarter of Kepler data.  TESS has also observed most of the
		cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2a.pdf}
			\includegraphics[width=0.469\textwidth]{f2b.pdf}
		}

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.}  {\it Top:} Color-absolute
		magnitude diagram of candidate \cn\ members, in addition to stars
		in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx 115$\,Myr),
		and the Gaia EDR3 Catalog of Nearby Stars (gray background).  The
		zoomed right panel highlights the pre-main-sequence.  The \cn\ and
		IC\,2602 are approximately the same isochronal age.  {\it Bottom:}
		TESS and Kepler stellar rotation period versus dereddened Gaia
		color, with the Pleiades and Praesepe (650\,Myr) shown for
		reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
		candidate \cn\ members are gyrochronally younger than the Pleiades; outliers are
		probably field interlopers.
		\label{fig:age}
	}
\end{figure*}

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}. 
Approximately 10 of the \cn\ stars appear as outliers above
the ``slow sequence''.  Assuming that they are all false positives
({\it i.e.}, field interlopers), our rotation period detection
fraction would be $\nrotgood/\nkinwithtessandcrowding \approx
\nfracprot\%$.   
The other stars are likely to be field contaminants.
A final possible confounding factor -- binarity -- is known to affect
the density of stars that fall beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f10a.pdf}
			\includegraphics[width=0.48\textwidth]{f10b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2.5V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the stacked NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia
    EDR3 renormalized unit weight error (RUWE) point estimates for
    candidate $\delta$\,Lyr cluster
    members from Figure~\ref{fig:XYZvtang}.  Since other members of the
    cluster with similar brightnesses have comparable degrees of
    photometric variability, the high RUWE independently suggests that Kepler\,1627
    is a binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=\textwidth]{f3a.pdf}
		}

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

@@

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 78\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the 30-minute
cadence \texttt{PDCSAP} light curve.  Nonastrophysical variability has
been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}. 
Cadences with non-zero quality flags (9\% of the data) have been omitted.
 The resulting photometry is dominated by
a quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  
Previous analyses have identified and
characterized the hidden transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us
with more precise stellar parameters than those previously available,
we opted to reanalyze the
light curve.

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and a white noise 
jitter ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in the bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top) and
purple (bottom).
The model parameters and their uncertainties, given in Table~\ref{tab:posterior}, are
broadly consistent with a mini-Neptune sized planet ($3.36\pm0.18\,R_\oplus$) on a close-in circular\footnote{ Our transit fitting
	yields $e<0.48$ at 2-$\sigma$; the constraints on the eccentricity are
	not particularly strong.} orbit around a G8V host star ($0.88 \pm 0.02
R_\odot$).  Our best-fit planet size is smaller than that
previously reported by \citet{morton_false_2016} and
\citet{berger_identifying_2018}, at 0.7-$\sigma$ and 1.2-$\sigma$
confidence respectively.  The former is explained by differing
assumptions about the stellar radius; the latter appears to be due to
differences in the measured transit depth, which could be linked to
the different methods used to account for the stellar rotation signal.

The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric
residual in the data relative to the model: the measured flux is 
high during the first half of transit, and low in the second half.  The
semi-amplitude of this deviation is $\approx50\,{\rm ppm}$, which
represents a $\approx 3\%$ distortion of the transit depth
($\approx1700\,{\rm ppm}$).  
Note that
while this asymmetry is within the 2-$\sigma$ model
uncertainties, the model has a jitter term that grows to
account for otherwise unmodeled white noise in the flux.  The
significance of the asymmetry is therefore best assessed in comparison
against the intrinsic out-of-transit scatter in the data, not the model
uncertainties.

To determine whether the asymmetry is a systematic caused by our stellar variability model,
we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.  
Appendix~\ref{app:asymmetry} includes a deeper analysis, and
finds that the asymmetry also seems to be robust to different methods of
data binning.  The most likely astrophysical explanations are
discussed in
Section~\ref{sec:conc}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f4a.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
		The time of each Kepler transit was measured, along with the local
		slope of the light curve.  The two quantities appear
		anti-correlated, which is most easily explained by starspot
		crossings during the first (second) half of transit inducing a
		positive (negative) TTV, provided that the orbit is prograde
		\citep{mazeh_time_2015}.  The units along the abscissa are most
		easily understood by considering that the stellar flux changes by
		$\sim$60\,ppt per half rotation period ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the main
Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   
Could the transit be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.  However,
this calculation was performed without knowledge of the low-mass stellar companion ($M_{\rm B}\approx
0.33\,M_\odot$).  
Validated planets have also previously been refuted \citep[{\it e.g.},][]{shporer_three_2017}.
We therefore reassessed
false positive scenarios in some detail.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile is
  asymmetric, and the individual transit times are correlated with the
  local light curve slope.
  We discuss possible explanations for each anomaly.
  More broadly applicable though is the fact that the $\delta$~Lyr
  cluster is one of $\sim$10$^3$ clusters whose properties have been
  clarified by Gaia.  Many other exoplanet hosts are candidate
  kinematic members of these clusters; their cluster memberships can
  be verified by measuring stellar rotation periods in the TESS full
  frame images.
\end{abstract}

@@

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{KounkelCovey2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Galactic positions and tangential velocities of stars in the
			$\delta$\,Lyr cluster.} Points are reported cluster members from
		\citet{KounkelCovey2019}.  
		The tangential velocities relative to
		\sn\ (lower-right) are computed assuming that every star has the same
		three-dimensional spatial velocity as \sn.
		Our analysis considers stars (black points)
		in the spatial and kinematic vicinity of Kepler\,1627 (yellow
		star).  The question of whether the other candidate cluster members
		(gray points) are part of the cluster is outside our scope.  The
		location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive,\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.}
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
		candidate cluster member selected from the catalog of \citet{KounkelCovey2019} based on its
		position and kinematics.
		Of the \nkinematic\ candidate cluster members, 58 have at least one
		quarter of Kepler data.  TESS has also observed most of the
		cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f3a.pdf}
			\includegraphics[width=0.469\textwidth]{f3b.pdf}
		}

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.}  {\it Top:} Color-absolute
		magnitude diagram of candidate \cn\ members, in addition to stars
		in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx 115$\,Myr),
		and the Gaia EDR3 Catalog of Nearby Stars (gray background).  The
		zoomed right panel highlights the pre-main-sequence.  The \cn\ and
		IC\,2602 are approximately the same isochronal age.  {\it Bottom:}
		TESS and Kepler stellar rotation period versus dereddened Gaia
		color, with the Pleiades and Praesepe (650\,Myr) shown for
		reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
		candidate \cn\ members are gyrochronally younger than the Pleiades; outliers are
		probably field interlopers.
		\label{fig:age}
	}
\end{figure*}

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}. 
Approximately 10 of the \cn\ stars appear as outliers above
the ``slow sequence''.  Assuming that they are all false positives
({\it i.e.}, field interlopers), our rotation period detection
fraction would be $\nrotgood/\nkinwithtessandcrowding \approx
\nfracprot\%$.   
The other stars are likely to be field contaminants.
A final possible confounding factor -- binarity -- is known to affect
the ``fast sequence'' of stars beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f4a.pdf}
			\includegraphics[width=0.48\textwidth]{f4b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2.5V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the stacked NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia
    EDR3 renormalized unit weight error (RUWE) point estimates for
    candidate $\delta$\,Lyr cluster
    members.  Since other members of the
    cluster with similar brightnesses have comparable degrees of
    photometric variability, the high RUWE independently suggests that Kepler\,1627
    is a binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=\textwidth]{f5a.pdf}
		}

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f5b.pdf}
			\includegraphics[width=0.5\textwidth]{f5c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

@@

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 78\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the 30-minute
cadence \texttt{PDCSAP} light curve.  Nonastrophysical variability has
been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}. 
Cadences with non-zero quality flags (9\% of the data) have been omitted.
 The resulting photometry is dominated by
a quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  
Previous analyses have identified and
characterized the smaller transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us
with more precise stellar parameters than those previously available,
we opted to reanalyze the
light curve.

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, \delta, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and a white noise 
jitter ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in the bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top) and
purple (bottom).
The model parameters and their uncertainties, given in Table~\ref{tab:posterior}, are
broadly consistent with a mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in circular\footnote{ Our transit fitting
	yields $e<0.48$ at 2-$\sigma$; the constraints on the eccentricity are
	not particularly strong.} orbit around a G8V host star ($0.88 \pm 0.02
R_\odot$).  This best-fit planet size is consistent with those
previously reported by \citet{morton_false_2016} and
\citet{berger_identifying_2018}, and corrects for the small
amount of flux dilution from Kepler\,1627B.
%at 0.3-$\sigma$ and 0.2-$\sigma$ respectively.

The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric
residual in the data relative to the model: the measured flux is 
high during the first half of transit, and low in the second half.  The
semi-amplitude of this deviation is $\approx50\,{\rm ppm}$, which
represents a $\approx 3\%$ distortion of the transit depth
($1759\pm62\,{\rm ppm}$).  
Note that
while this asymmetry is within the 2-$\sigma$ model
uncertainties, the model has a jitter term that grows to
account for otherwise unmodeled white noise in the flux.  The
significance of the asymmetry is therefore best assessed in comparison
against the intrinsic out-of-transit scatter in the data, not the model
uncertainties.

To determine whether the asymmetry is a systematic caused by our stellar variability model,
we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.  
Appendix~\ref{app:asymmetry} includes a deeper analysis, and
finds that the asymmetry also seems to be robust to different methods of
data binning in time and by local light curve slope.  The most likely
astrophysical explanations are discussed in Section~\ref{sec:conc}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
		The time of each Kepler transit was measured, along with the local
		slope of the light curve.  The two quantities appear
		anti-correlated, which is most easily explained by starspot
		crossings during the first (second) half of transit inducing a
		positive (negative) TTV, provided that the orbit is prograde
		\citep{mazeh_time_2015}.  The units along the abscissa can
		be understood by considering that the stellar flux changes by
		$\sim$60\,ppt per half rotation period ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the main
Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   
Could the transit be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx$$10^{-5}$.  However,
this calculation was performed without knowledge of the low-mass stellar companion ($M_{\rm B}\approx
0.33\,M_\odot$).  
Validated planets have also previously been refuted \citep[{\it e.g.},][]{shporer_three_2017}.
We therefore reassessed
false positive scenarios in some detail.

% (0.7-2.0\% V-band to G-band dmag difference from EEM table; NOTE
% could determine using model spectra)
As an initial plausibility check,
Kepler\,1627B contributes 1\% to 2\% of the total flux observed in
the Kepler aperture.  
For the sake of argument, assume the former value.
The observed transit has a depth of $\approx$0.18\%.  A
18\% deep eclipse of the secondary star would therefore be needed to
produce a signal with the appropriate depth.  The shape of the
transit signal however requires the impact parameter to be below 0.77
(2-$\sigma$); the tertiary transiting the secondary would
therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
%Assuming a $\approx 0.46R_\odot$ radius of the imaged secondary
%from the \citet{baraffe_new_2015} models, this
%would imply a tertiary stellar radius of $\approx 0.2R_\odot$.
This
yields a contradiction:  this scenario would require an ingress and
egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.
